---
title: "p8105_hw6_kk3154"
author: "Kristen King"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
  echo = TRUE, 
  warning = FALSE, 
  fig.width = 8, 
  fig.height = 6, 
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis", 
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 1 - Linear Regression Model for Birthweight

Loading and cleaning the birthweight data.

```{r}
bw_df = read_csv(file = "./data/birthweight.csv", show_col_types = FALSE)

bw_df = bw_df %>% 
  mutate(
    babysex = factor(babysex, levels = c(1, 2), labels = c("male", "female")), 
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("White", "Black", "Asian", "Puerto Rican", "Other", "Unknown")),
    malform = factor(malform, levels = c(0, 1), labels = c("absent", "present")), 
    mrace = factor(mrace, levels = c(1, 2, 3, 4, 8), labels = c("White", "Black", "Asian", "Puerto Rican", "Other")) 
  )

skimr::skim(bw_df)
```

Building a linear model (Model 1).

Identifying variables for inclusion by running all bivariable (unadjusted) models and removing variables with a p-value > 0.1 (for categorical variables, remove only if p > 0.1 for all levels).

```{r}
predictors = colnames(select(bw_df, -bwt))

unadj_function = function(preds) {
  form = paste("bwt ~", preds)
  lm(as.formula(form), data = bw_df)
}

unadj_models = tibble(
  names = predictors, 
  models = map(predictors, unadj_function), 
  results = map(models, broom::tidy)) %>% 
  select(names, results) %>% 
  unnest(results) %>% 
  filter(term != "(Intercept)") %>% 
  knitr::kable(digits = 3)

unadj_models
```

Model 1 will include all predictor variables in the dataset, except for malform, menarche, parity, pnumlbw, and pnumsga based on bivariable analyses. I will also exclude ppwt and mheight since these are presumably already incorporated in the calculation of ppbmi.

```{r}
fit_m1 = lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + momage + mrace + ppbmi + smoken + wtgain, data = bw_df) 

fit_m1 %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

Plotting residuals against fitted values for Model 1:

```{r}
bw_df %>% 
  modelr::add_residuals(fit_m1) %>% 
  modelr::add_predictions(fit_m1) %>% 
  ggplot(aes(x = pred, y = resid)) + 
  geom_point() + 
  labs(
    title = "Model 1: Residuals vs. Fitted Values", 
    y = "Residual",
    x = "Fitted Value")
```

Comparing Model 1 to two additional models using cross-validation.

* Model 2: Main Effects only (length at birth and gestational age)

* Model 3: Interaction model (head circumference, length, sex + 3-way interaction)

```{r}
library(modelr)
library(purrr)

cv_df = 
  crossv_mc(bw_df, 100, test = .2) %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )

cv_df = 
  cv_df %>% 
  mutate(
    m1 = map(lm(bwt ~ babysex + bhead + blength + delwt + fincome + frace + gaweeks + momage + mrace + ppbmi + smoken + wtgain, data = bw_df, data = train)), 
    m2 = map(lm(bwt ~ blength + gaweeks, data = train)), 
    m3 = map(lm(bwt ~ bhead * blength * babysex, data = train))
  ) %>% 
  mutate(
    rmse_m1 = map2_dbl(.x = m1, .y = test, ~rmse(model = .x, data = .y)), 
    rmse_m2 = map2_dbl(.x = m2, .y = test, ~rmse(model = .x, data = .y)),
    rmse_m3 = map2_dbl(.x = m3, .y = test, ~rmse(model = .x, data = .y)),
  )

cv_df %>% 
  select(.id, starts_with("rmse")) %>% 
  pivot_longer(
    rmse_m1:rmse_m3,
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_boxplot()
```

## Problem 2 - Bootstrapping Central Park Weather Data

Loading 2017 Central Park weather data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```



